Predicting Internet Path Dynamics and Performance with Machine Learning

### 2017-12-20 paper-tex/paper.tex
method lstm

	\begin{figure}[tp]
		\centering
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/total_life_8}
			\label{fig:3.1a}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/total_life_20}
			\label{fig:3.1b}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/total_life_21}
			\label{fig:3.1c}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/total_life_30}
			\label{fig:3.1d}
		\end{subfigure}
		\caption{Temporal patterns of route life among 4 different paths.}
		\label{fig:3.1}
	\end{figure}

	\begin{figure}[!htp]
		\centering
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/route_change_8}
			\label{fig:3.2a}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/route_change_20}
			\label{fig:3.2b}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/route_change_21}
			\label{fig:3.2c}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/route_change_30}
			\label{fig:3.2d}
		\end{subfigure}
		\caption{Temporal patterns of the number of route changes among 4 different paths.}
		\label{fig:3.2}
	\end{figure}

	\begin{figure}[!htp]
		\centering
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/RTT_8}
			\label{fig:3.3a}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/RTT_20}
			\label{fig:3.3b}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/RTT_21}
			\label{fig:3.3c}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth]{fig/RTT_30}
			\label{fig:3.3d}
		\end{subfigure}
		\caption{Temporal patterns of round trip time among 4 different paths.}
		\label{fig:3.3}
	\end{figure}

@@

>>>>

	\begin{figure}[tp]
		\centering
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/total_life_8}
			\label{fig:3.1a}
		\end{subfigure}
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/total_life_20}
			\label{fig:3.1b}
		\end{subfigure}
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/total_life_21}
			\label{fig:3.1c}
		\end{subfigure}
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/total_life_30}
			\label{fig:3.1d}
		\end{subfigure}
		\caption{Temporal patterns of route life among 4 different paths.}
		\label{fig:3.1}
	\end{figure}

	\begin{figure}[!htp]
		\centering
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/route_change_8}
			\label{fig:3.2a}
		\end{subfigure}
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/route_change_20}
			\label{fig:3.2b}
		\end{subfigure}
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/route_change_21}
			\label{fig:3.2c}
		\end{subfigure}
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/route_change_30}
			\label{fig:3.2d}
		\end{subfigure}
		\caption{Temporal patterns of the number of route changes among 4 different paths.}
		\label{fig:3.2}
	\end{figure}

	\begin{figure}[!htp]
		\centering
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/RTT_8}
			\label{fig:3.3a}
		\end{subfigure}
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/RTT_20}
			\label{fig:3.3b}
		\end{subfigure}
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/RTT_21}
			\label{fig:3.3c}
		\end{subfigure}
		\begin{subfigure}[t]{0.4\linewidth}
			\centering
			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/RTT_30}
			\label{fig:3.3d}
		\end{subfigure}
		\caption{Temporal patterns of round trip time among 4 different paths.}
		\label{fig:3.3}
	\end{figure}

@@

	\subsection{LSTM Model}
	In order to leverage the prediction targets' character of temporal locality, we further use LSTM to do time series modeling. More formally, we take $t-1$ most recent \texttt{traceroute} measurements features $(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-2}},\mathbf{x_{t-1}})$and the current \texttt{traceroute} measurement feature $\mathbf{x_t}$ together as the input,i.e.,$\mathbf{X}=(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-1}},\mathbf{x_{t}})$ And the out put is a single scalar $\hat{y}$ which is supposed to be the prediction of the target $y$.
	Let $G_{\theta}(\mathbf{x_i},\mathbf{h_i})$ the $\theta$ parameterized LSTM, we have:
	\begin{equation}
	\mathbf{h_{i+1}}=G_{\theta}(\mathbf{x_i},\mathbf{h_i}),
	\end{equation}iteratively. and when we have the $\mathbf{h_{t}}$, we calculate our final prediction $\hat{y}$ by a fully connected layer with parameter $\mathbf{W}$:
	\begin{equation}
	\hat{y}=\mathbf{W}\cdot\mathbf{h_t},
	\end{equation}
	and the loss function is:
	\begin{equation}
	\mathcal{L}=\frac{1}{n}\sum_{i=1}^{n}(y_i-\hat{y_i})^2.
	\end{equation}
	The training objective is to minimize $\mathcal{L}$.
